Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-28 ms.tex
added a plot w/ residuals revealing that the timing might be changing.

We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009-05-13 and ending on 2013-04-08 for a total of 1425 days or 2181.5 orbits.
The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 with thin the $\pm$ 0.28 window.
All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
The secondary eclipses are used to quantify the noise in the transit depths.

We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
The constraint is even tighter assuming a circular orbit.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
Here the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data.
}\label{fig:secEclipse}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit (Right).}\label{fig:kepPCA}
\end{centering}
\end{figure*}

>>>>

We downloaded all 17 quarters of Kepler Long-Cadence data from the MAST archive beginning on 2009-05-13 and ending on 2013-04-08 for a total of 1425 days or 2181.5 orbits.
The Kepler data were examined for one transit or secondary eclipse at a time with a window of $\pm$0.28 in orbital phase.
A quadratic baseline is fit to all the points before a phase of 0.12 and after a phase of 0.15 within the $\pm$ 0.28 window.
All points are divided by this baseline to produce a normalized flux transit or eclipse profile.
The secondary eclipses are used to quantify the noise in the transit depths.

We confirm the result of \citet{vanWerkhoven2014} that no secondary eclipse is detected a at $\lesssim 50$ ppm, seen in Figure \ref{fig:secEclipse}. 
We then use the secondary eclipses as a way to characterize the noise of the primary eclipses.
Both have the same quadratic baseline removal process over the same time intervals.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{No secondary eclipse ( $\lesssim$ 50 ppm) is detected from a phase range of -0.25 to 0.75, even with 17 quarters (4 years) of Kepler Long Cadence data.
Here, the data are binned to orbital phases of 0.1 or 1.5 minutes and errors calculated from the standard error in the mean of the data within a bin.
}\label{fig:secEclipse}
\end{centering}
\end{figure*}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/residual_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Top Left) and model fit (Top Right).
The residual is shown with a different scaling below.
In this fitting process, no adjustments were made for timing, which is apparent in the residuals.}\label{fig:kepPCA}
\end{centering}
\end{figure*}
